\begin{thebibliography}{99}
	\bibitem{telexistence}
S.Tachi, K.Tanie, K.Komoriya, M.Kaneko: Tele-existence (I): Design and Evaluation of a Visual Display with Sensation of Presence; 
Theory and Practice of Robots and Manipulators pp 245-254

\bibitem{factorio}
舘 章:テレロボティクスとテレイグジスタンス; 計測と制御,28巻,12号,p1059-1064

\bibitem{sprots}
Kiana Calagari: Sports VR Content Generation from Regular Camera Feeds; MM'17 Proceedings of the 25th ACM international conference on Multimedia
Pages 699-707

\bibitem{oculus}
Marjolijn Ruyg: Virtual Reality for the Web: Oculus Rift, 2014.

\bibitem{vrmodel}
Randy Hudson: PanoVR SDK―a software development kit for integrating photo-realistic panoramic images and 3-D graphical objects into virtual worlds; VRST ’97 Proceedings of the ACM symposium on Virtual reality soft- ware and technology, Pages 147-154.

\bibitem{ogasawara}
テレイグジスタンス (R) 技術を活用した遠隔操作ロボットの量産型プロトタイプMODEL Hを開発 および、ロボット旅行体験イベントの実施,Telexistence株式会社,KDDI株式会社\\
https://news.kddi.com/kddi/corporate/newsrelease/2018/05/29/3168.html

\bibitem{kinect}
Kinect
https://developer.microsoft.com/ja-jp/windows/kinect,Microsoft.

\bibitem{photon}
Photon Unity Cloud;\\ https://www.photonengine.com/en-US/photon,ユニティ・テクノロジーズ.

\bibitem{gsv}
Google Street View,\\
https://www.google.co.jp/intl/ja/streetview/,Google.

\bibitem{doorcom}
濵上 宏樹, 吉野 孝: ドアコムAR：ポータルを用いた空間接続表現手法
による対話相手の存在感の強化; 情報処理学会インタラクション2018, 

\bibitem{Hololens}
Hololens,\\
https://www.microsoft.com/ja-jp/hololens,Microsoft.

\bibitem{holopotation}
Ben Cutler, Spencer Fowers, Wayne Chang, Samuel Ogden:Holoportation;\\ https://www.microsoft.com/en-us/research/project/holoportation-3/

\bibitem{kiosk}
Devid Debult. SimSensei Kiosk: A Virtual Human In- terviewer for Healthcare Decision Support. Proceedings of the 13th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2014), May 5-9, 2014.

\bibitem{digitalemily}
Oleg Alexander. The Digital Emily Project: Achieving a Photorealistic Digital Actor. IEEE Computer Graphics and Applications, 2010.

\bibitem{maryam}
Maryam Mustafa. How Human Am I? EEG-based Eval- uation of Animated Virtual Characters. CHI 2017, May 06 - May 11, 2017, Denver, CO, USA, 2017.

\bibitem{shenchang}
Shenchang Eric Chen: QuickTime VR -An Image-Based Approach to Virtual Environment Navigation; SIGGRAPH ’95 Proceedings of the 22nd annual conference on Computer graphics and interactive techniques, Pages 29-38.

\bibitem{fitnamo}
 Edward Nguyan. Fitnamo: Using BodyData to Encourage Exercise through Google Glass CHI 2014, One of a CHInd, Toronto, ON, Canada.

\bibitem{pokego}
ポケモンGO,\\
https://www.pokemongo.jp/ ,https://www.pokemongo.jp/, ナイアンティック,株式会社ポケモン.

\bibitem{mrgame}
Michael Bonfert. 2017. Augmented Invaders: A Mixed Reality Multiplayer Outdoor Game. VRST ’17, November 8-10.

\bibitem{holotour}
David Haley, Danny Askew,Jason Syltebo,Travis Steiner : Case study - Capturing and creating content for HoloTour;\\
https://docs.microsoft.com/en-us/windows/mixed-reality/case-study-capturing-and-creating-content-for-holotour

\bibitem{Unity}
Unity,\\
https://unity3d.com/jp,ユニティ・テクノロジーズ.


\bibitem{json}
JSON,\\
https://www.json.org/json-ja.html

\bibitem{googlemapsapi}
Google Maps API,\\
https://cloud.google.com/maps-platform/?hl=ja,Google.

\bibitem{svrule}
Google Street View 認定要件,\\
https://www.google.co.jp/intl/ja/streetview/earn/, Google.

\bibitem{GSVpano}
GSVPano;\\
https://juampi92.github.io/ GSVPano/.

\bibitem{unitychan}
Unityちゃん,Unity Technologies Japan/UCL\\
https://assetstore.unity.com/packages/3d/characters/unity-chan-model-18705

\bibitem{pq}
Witmer, Singer: The factor structure of the Presence Questionnaire; 298- 312.

\bibitem{itq}
Witmer,Singer: Measuring presence in virtual environments: A presence questionnaire. Presence : Teleoperators and Virtual Environments; 225-240.

%	\bibitem{easing}Andrey Sitnik. ``Easing Function 早見表'' \\ \href{http://easings.net/ja}{http://easings.net/ja}

\end{thebibliography}
